%-------------------------
% CV in LaTeX (Jake template based)
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{6pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.65in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlist[itemize]{leftmargin=0.15in, topsep=2pt, itemsep=1pt, parsep=0pt, partopsep=0pt}
\setlist[enumerate]{leftmargin=0.15in, topsep=2pt, itemsep=2pt, parsep=0pt, partopsep=0pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\newcommand{\cofa}{\textsuperscript{*}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Haochen Sun} \\ \vspace{1pt}
    \small \href{mailto:haochen.sun@uwaterloo.ca}{\underline{haochen.sun@uwaterloo.ca}} $|$
    \href{https://jvhs0706.github.io}{\underline{jvhs0706.github.io}} $|$
    \href{https://scholar.google.com/citations?user=Kwlbf1kAAAAJ}{\underline{Google Scholar}} $|$
  \href{https://ca.linkedin.com/in/haochen-sun-3131201a0}{\underline{LinkedIn}} \\ \vspace{1pt}
  \small University of Waterloo, 200 University Avenue West, Waterloo, Ontario, N2L 3G1, Canada
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Sep 2022 -- Present}
      {PhD in Computer Science}{Waterloo, Canada}
      \resumeItemListStart
        \resumeItem{Supervisor: Prof. Xi He}
        \resumeItem{Research Focus: Security and privacy in machine learning and data management}
        \resumeItem{Honors and Awards: David R. Cheriton Graduate Scholarship}
      \resumeItemListEnd

    \resumeSubheading
      {The Hong Kong University of Science and Technology (HKUST)}{Sep 2018 -- Jul 2022}
      {BSc in Data Science and Technology, and in Computer Science}{Hong Kong, China}
      \resumeItemListStart
        \resumeItem{GPA: 3.888/4.3 | Major GPA: 4.041/4.3}
        \resumeItem{Honors and Awards: Chern Class Scholarship (Department of Mathematics), Zhiyuan Scholarship (China Soong Ching Ling Foundation), HKUST Scholarship Scheme for Continuing Undergraduates, Dean's List}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------RESEARCH EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Faithfulness of Differential Privacy Mechanism Execution}{May 2024 -- Present}
      {PhD Research Project (with Prof. Xi He)}{University of Waterloo}
      \resumeItemListStart
        \resumeItem{Investigating vulnerabilities from unfaithful execution of differential privacy mechanisms, focusing on additional privacy leakage incurred, and defenses to ensure execution integrity.}
      \resumeItemListEnd

    \resumeSubheading
      {Zero-Knowledge Deep Learning}{Sep 2022 -- Apr 2024}
      {with Prof. Hongyang Zhang}{University of Waterloo}
      \resumeItemListStart
        \resumeItem{Specialized zero-knowledge proof (ZKP) protocols for deep learning with CUDA implementations.}
        \resumeItem{The first working ZKP scheme for 13B-parameter LLMs and for training 10M-parameter neural networks.}
      \resumeItemListEnd

    \resumeSubheading
      {Air Pollution Forecasting with Deep Learning}{Jan 2020 -- Nov 2022}
      {Undergraduate Research and RA (with Profs. Jimmy Fung and Xingcheng Lu)}{HKUST}
      \resumeItemListStart
        \resumeItem{Designed deep learning architectures for modeling the spatio-temporal distribution of air pollutants.}
        \resumeItem{Improved regional air pollution forecasting accuracy by 30\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
\begin{enumerate}
  \small
  \item \textbf{(SIGMOD 2026 Best Paper Award)} \underline{Haochen Sun} and Xi He. ``GPM: The Gaussian Pancake Mechanism for Planting Undetectable Backdoors in Differential Privacy.'' \textit{Proceedings of the ACM on Management of Data (PACMMOD)}, 2026.
  \item \underline{Haochen Sun} and Xi He. ``VDDP: Verifiable Distributed Differential Privacy under the Client--Server--Verifier Setup.'' \textit{Theory and Practice of Differential Privacy (TPDP)}, 2026.
  \item \underline{Haochen Sun}\cofa, Shufan Zhang\cofa, Karl Knopf\cofa, Shubhankar Mohapatra, Wei Pang, Calvin Wang, Yingke Wang, Masoumeh Shafieinejad, David Emerson, and Xi He. ``FedDPSyn: Federated Tabular Data Synthesis with Computational Differential Privacy.'' \textit{Theory and Practice of Differential Privacy (TPDP)}, 2025.
  \item \underline{Haochen Sun}, Jason Li, and Hongyang Zhang. ``zkLLM: Zero-Knowledge Proofs for Large Language Models.'' \textit{ACM Conference on Computer and Communications Security (CCS)}, 2024.
  \item \underline{Haochen Sun}, Tonghe Bai, Jason Li, and Hongyang Zhang. ``zkDL: Efficient Zero-Knowledge Proofs of Deep Learning Training.'' \textit{IEEE Transactions on Information Forensics and Security (TIFS)}, 2024.
  \item \underline{Haochen Sun}, Jimmy C. H. Fung, Yiang Chen, Zhenning Li, Dehao Yuan, Wanying Chen, and Xingcheng Lu. ``Development of an LSTM broadcasting deep-learning framework for regional air pollution forecast improvement.'' \textit{Geoscientific Model Development (GMD)}, 2022.
  \item \underline{Haochen Sun}, Jimmy C. H. Fung, Yiang Chen, Wanying Chen, Zhenning Li, Yeqi Huang, Changqing Lin, Mingyun Hu, and Xingcheng Lu. ``Improvement of $\text{PM}_{2.5}$ and $\text{O}_{3}$ forecasting by integration of 3D numerical simulation with deep learning techniques.'' \textit{Sustainable Cities and Society (SCS)}, 2021.
\end{enumerate}

%-----------ACADEMIC SERVICES-----------
\section{Academic Services}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    \item \textbf{(Sub)Reviewer:} Conferences: CCS, SIGMOD, VLDB, NeurIPS, SaTML, AISTATS; Journals: TDSC, TMLR, TKDE.
    \item \textbf{Teaching Assistant, University of Waterloo:} Courses: CS~116, CS~135, CS~246, CS~330, CS~480.
  }
\end{itemize}

%-------------------------------------------
\end{document}
