%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------

\newcommand{\cofa}{\textsuperscript{*}}
\cvsection{Publications}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries2}
\begin{cvenumerate}
    \item \textbf{(SIGMOD 2026 Best Paper Award)} \underline{Haochen Sun} and Xi He. ``GPM: The Gaussian Pancake Mechanism for Planting Undetectable Backdoors in Differential Privacy.'' \textit{Proceedings of the ACM on Management of Data (PACMMOD)}, 2026.
    \item \underline{Haochen Sun} and Xi He. ``VDDP: Verifiable Distributed Differential Privacy under the Client--Server--Verifier Setup.'' \textit{Theory and Practice of Differential Privacy (TPDP)}, 2026.
    \item \underline{Haochen Sun}\cofa, Shufan Zhang\cofa, Karl Knopf\cofa, Shubhankar Mohapatra, Wei Pang, Calvin Wang, Yingke Wang, Masoumeh Shafieinejad, David Emerson, and Xi He. ``FedDPSyn: Federated Tabular Data Synthesis with Computational Differential Privacy.'' \textit{Theory and Practice of Differential Privacy (TPDP)}, 2025.
    \item \underline{Haochen Sun}, Jason Li, and Hongyang Zhang. ``zkLLM: Zero-Knowledge Proofs for Large Language Models.'' \textit{ACM Conference on Computer and Communications Security (CCS)}, 2024.
    \item \underline{Haochen Sun}, Tonghe Bai, Jason Li, and Hongyang Zhang. ``zkDL: Efficient Zero-Knowledge Proofs of Deep Learning Training.'' \textit{IEEE Transactions on Information Forensics and Security (TIFS)}, 2024.
    \item \underline{Haochen Sun}, Jimmy C. H. Fung, Yiang Chen, Zhenning Li, Dehao Yuan, Wanying Chen, and Xingcheng Lu. ``Development of an LSTM broadcasting deep-learning framework for regional air pollution forecast improvement.'' \textit{Geoscientific Model Development (GMD)}, 2022.
    \item \underline{Haochen Sun}, Jimmy C. H. Fung, Yiang Chen, Wanying Chen, Zhenning Li, Yeqi Huang, Changqing Lin, Mingyun Hu, and Xingcheng Lu. ``Improvement of $\text{PM}_{2.5}$ and $\text{O}_{3}$ forecasting by integration of 3D numerical simulation with deep learning techniques.'' \textit{Sustainable Cities and Society (SCS)}, 2021.
\end{cvenumerate}
\end{cventries2}
